A Two-Infall Star Formation History with Outflows and Radial Migration

### 2024-09-06 src/tex/ms.tex
Updates from Overleaf

The two-infall model has long been proposed to explain the high- and low-$\alpha$ sequences observed in the Milky Way disk.

@@

\begin{table*}
    \centering
    \caption{Yields.}
    \label{tab:yields}
    \include{output/yields.tex}
\end{table*}

@@

>>>>

The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks. The infall history of any given region of the disk is described by two successive, exponentially declining bursts, whose timescale may vary as a function of radius. The first infall, which forms the thick disk, has a short timescale, typically on the order of $\sim1$ Gyr. The second infall forms the thin disk and has a much longer timescale, typically $\sim4-10$ Gyr.

% Summary of two-infall papers
\citet{matteucci_galactic_1989} modeled the galaxy with a two-component model, a one-zone model for the halo and concentric shell zones for the disk. They used a simple exponential gas infall (so not yet a two-infall model), where the infall timescale increased proportionally with radius. They studied cases with primordial and pre-enriched gas infall, finding that the former produces a more realistic metallicity distribution in the Solar neighborhood. Their inside-out disk evolution produced good agreement with observed abundance gradients.

\citet{chiappini_chemical_1997} presented the first two-infall model of the MW disk. They adopted an inside-out prescription for the formation of the thin disk, with the timescale of the second infall varying with radius. Their model parameters were constrained by the observed

% Radial gas flows
Some two-infall studies \citep[e.g.,][]{palla_chemical_2020,palla_mapping_2024} implement inward radial gas flows with velocity $\sim1$ km s$^{-1}$ in order to reproduce the radial abundance gradient without Galactic outflows.

@@

\begin{table}
    \centering
    \caption{Yields.}
    \label{tab:yields}
    \include{output/yields.tex}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_sfr.pdf}
    \caption{Caption.}
    \label{fig:onezone-sfr}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params.pdf}
    \caption{Caption.}
    \label{fig:onezone-params}
\end{figure*}
